Atomify - a live LAMMPS visualizer

### 2016-10-10 ms.tex
Wrote better abstract and some introduction

\documentclass[aps,pre,twocolumn,letterpaper,floatfix,showpacs]{revtex4}
\usepackage{graphicx} 
\usepackage{amsmath,amssymb,amsfonts} 
\usepackage{mathtools}
\usepackage{pdfpages}
\usepackage{afterpage}
\usepackage[hidelinks]{hyperref} 
\usepackage{epstopdf}
\begin{document}
\title{Atomify - a live LAMMPS visualizer}
%\author{A. Hafreager, S-A. Dragly, A. Malthe-S\oe renssen$^1$}
\email{anders.hafreager@fys.uio.no}
\author{Svenn-Arne Dragly $^{1}$} 
\author{Anders Malthe-S\o renssen $^1$}
\affiliation{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway }
\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract} 
Atomify is a new tool simplifying the workflow when working with LAMMPS. It combines script editing, running simulations and visualizing into one single application by running an instance of a LAMMPS object with direct access to the simulation data in memory. Live plotting of computes in LAMMPS can easily be shown by an easy-to-use GUI. High end hardware is able to run Atomify with live simulations of millions of atoms with a modern, high quality rendering technique. Atomify supports accelerated simulations with OpenMP, GPU and Xeon Phi. The program is built with Qt and is distributed as open-source software under the GPL license. 
\end{abstract}

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Molecular dynamics has become a standard technique for simulating atoms in a broad range of fields. It is used to understand how liquids, solids and gases behave in problems relevant for physics, chemistry and biology.

\section{Installation}
The installation of atomify can be done in many ways. The easiest ones are by using the App Store for your operating system (Ubuntu and Mac OSX currently supported). If you want to download and compile the software yourself, you will need Qt Creator (supporting Qt 5.7).
\subsection{Mac App Store}
Atomify is available as free software in the Mac App Store. 
\subsection{Homebrew on Mac}
brew install atomify

\subsection{Ubuntu}
sudo apt-get install atomify

\section{Application}
Atomify is a rather small code built on Qt. All GUI is defined in QML whereas the backend of the program communicating with LAMMPS is written in c++. Simply put, Atomify runs an instance of a LAMMPS object enabling the user to visualize the current state of LAMMPS and interact with LAMMPS while the simulation is running.

@@

\subsection{Rendering techniques}
Simulations of atoms are often visualized as spheres and cylinders. The spheres represent the atoms while the cylinders represent the bonds between the atoms. This way the molecular structure is much easier to see and understand. In popular visualization tools like VMD, the spheres and cylinders are built up by many triangles connected so they form the geometrical object of interest. The problem with this rendering technique is that each sphere needs many triangles in order to look spherical. This significantly reduces the rendering performance. A common technique to overcome this problem is to use billboards. Billboards are planes made up by two triangles with surface normal parallel to the vector pointing towards the camera. By doing proper shading, the billboards can mimick the spheres and cylinders so they look realistic.

\subsubsection*{Pipeline}
When rendering one often wants to modify the data from LAMMPS before it is visualized. Examples are periodic images of the simulation, slicing and coloring. We have been inspired by the pipeline used in Ovito where the data flows through several \textit{modifiers}, each modifying the visualization data before the data is converted to a format for the GPU.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{bibliography}

%\begin{thebibliography}{9}

%\bibitem[Groeneboom2014]{groeneboom2014} Groeneboom, N.~E., \& Dahle, H.\ 2014, \apj, 783, 138

%\end{thebibliography}

>>>>

\documentclass[aps,pre,twocolumn,letterpaper,floatfix,showpacs]{revtex4}
\usepackage{graphicx} 
\usepackage{amsmath,amssymb,amsfonts} 
\usepackage{mathtools}
\usepackage{pdfpages}
\usepackage{afterpage}
\usepackage[hidelinks]{hyperref} 
\usepackage{epstopdf}
\begin{document}
\title{Atomify - a live LAMMPS visualizer}
\author{Anders Hafreager$^1$}
\author{Svenn-Arne Dragly$^{1}$} 
\author{Anders Malthe-S\o renssen$^1$}
\affiliation{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway }
\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract} 
The typical workflow when developing LAMMPS scripts includes working with several programs. A text editor is needed to modify the scripts, the terminal to run the simulation, and programs like VMD or Ovito to visualize the system over time. If physical quantities are computed, the data is often plotted with MATLAB or Python. This is a tedious process, especially for teaching purposes and for people who are new to LAMMPS. 
We here introduce Atomify; a high performance live visualizer for LAMMPS simulations, with stunning graphics able to simulate and render more than 250000 atoms with excellent frame rate on modern hardware. Atomify supports OpenMP acceleration, live plotting of LAMMPS variables and computes, and an easy-to-use code editor in one single program. Direct access to the powerful machinery already built into LAMMPS allows easy access to advanced physical quantities. Atomify is open source software (GPL) written in C++, built on top of Qt. 
\end{abstract}

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Molecular dynamics has become a standard technique for simulating atoms and molecules in a broad range of fields. Over the years, increasingly sophisticated methods have been developed. With the large number of force fields, advanced techniques and GPU acceleration, implementing a good molecular dynamics program from scratch a challenging task. While many people at some point write their own code, most end up using one of the many available codes\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}} such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}. Both of these codes has been developed for more than two decades and contains more than one million lines of code each.

When

\section{Features}

\section{Implementation}
Atomify is a rather small code built on Qt. All GUI is defined in QML whereas the backend of the program communicating with LAMMPS is written in c++. Simply put, Atomify runs an instance of a LAMMPS object enabling the user to visualize the current state of LAMMPS and interact with LAMMPS while the simulation is running.

@@

\subsection{Data pipeline}
When rendering one often wants to modify the data from LAMMPS before it is visualized. Examples are periodic images of the simulation, slicing and coloring. We have been inspired by the pipeline used in Ovito where the data flows through several \textit{modifiers}, each modifying the visualization data before the data is converted to a format for the GPU.

\subsection{Rendering techniques}
Simulations of atoms are often visualized using spheres and cylinders. The spheres represent the atoms while the cylinders represent the bonds between the atoms. This way the molecular structure is easy to understand. In many visualization tools, the spheres and cylinders are built up by many triangles connected so they form the geometrical object of interest. The problem with this rendering technique is that each sphere needs many triangles in order to look spherical. This significantly reduces the rendering performance. A common technique to overcome this problem is to use billboards. Billboards are planes made up by two triangles with surface normal parallel to the vector pointing towards the camera. By doing proper shading, the billboards can mimick the spheres and cylinders so they look realistic.

@@

\section{Case study}

@@

\bibliographystyle{plain}
\bibliography{Remote}
